Mining Software Repositories for Contextual Information of Code Clones

### 2019-11-29 cefp/paper.tex
Updates from Overleaf

\keywords{Code Clones \and MSR \and Clone Relation \and Inheritance \and Object-Oriented Programming.}
\end{abstract}
%
%
%
\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.

\begin{figure}[H]
  \centering
    \includegraphics[width=0.8\columnwidth]{img/context}
    \caption{Abstract representation of clone classes and clone instances.}
  \label{fig:clonecontext}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

\subsection{Tool Validation}
We have validated the correctness of CloneRefactor through unit tests and empirical validation. First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases. These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they are correctly identified. Next, we run the tool over the corpus and manually verify samples of the acquired results. This way, we check the correctness of the identified clones, their context, and their proposed refactoring.

>>>>

\keywords{Code Clones \and MSR \and Clone Relation \and Inheritance \and Object-Oriented Programming.}
\end{abstract}
%
%
%
\section{Introduction}

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.

\begin{figure}[H]
  \centering
    \includegraphics[width=1\columnwidth]{img/context}
    \caption{Abstract representation of clone classes and clone instances.}
  \label{fig:clonecontext}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.7\columnwidth]{img/Relation}
      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

\subsection{Tool Validation}
We have validated the correctness of CloneRefactor through unit tests and empirical validation. First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases. These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup}), to see whether they are correctly identified. Next, we run the tool over the corpus and manually verify samples of the acquired results. This way, we check the correctness of the identified clones, their context, and their proposed refactoring.
